The hydra and the rooster

### 2020-07-25 latex/chapter-ordinals.tex
redaction introduction to ordinals

\subsubsection{Examples}

@@

More complex examples will be developped in further sections or chapters. For instance,
a notation system for ordinals less than $\epsilon_0$ is presented in chapter~\ref{chap:T1}.
Notation systems for $\omega+\omega$, $\omega^2$, etc. will be given in the next paragraphs.

>>>>

\subsection{Examples of Notation systems}

\subsubsection{The ordinal \texorpdfstring{$\omega$}{omega}}

@@

In order to build an instance of \texttt{ON}, we have to verify that \texttt{lt} is a well-founded strict order and define a correct comparison function.

\begin{Coqsrc}
Instance lt_strorder : StrictOrder lt.

Lemma lt_wf : well_founded lt.
Proof. apply wf_disjoint_sum; apply lt_wf. Qed.

Definition compare (alpha beta: t) : comparison :=
   match alpha, beta with
     inl _, inr _ => Lt
   | inl n, inl p | inr n, inr p => Nat.compare n p
   | inr _, inl _ => Gt
  end.

Lemma compare_correct alpha beta :
    CompareSpec (alpha = beta) (lt alpha beta) (lt beta alpha)
              (compare alpha beta).

Instance OmegaPlusOmega : ON lt compare.
Proof.
  split.
  - apply lt_strorder.
  - apply lt_wf.
  - apply compare_correct.
Qed.

More complex examples will be developped in further sections or chapters. For instance,
a notation system for ordinals less than $\epsilon_0$ is presented in chapter~\ref{chap:T1}.
